Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-18 bbbq_article.tex
Confidence interval for plot2a only

  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles
    that overlap with TMHs that are presented.
    Alleles are listed in Table \ref{tab:haplotype_abbreviations}).
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    \textbf{(B)} 
    MHC ligands from IEDB binding to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay. \textbf{GEER: zie comment in main text: wellicht rode horizontale streep bij verwachtingswaarde, net als in Fig 1A? Maakt manuscript veel duidelijker}
    The pair of horizontal red lines in each plot indicate the lower and upper bound 
    of the 99\% confidence interval.
  }
  \label{fig:elution}
\end{figure}

>>>>

  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles
    that overlap with TMHs that are presented.
    Alleles are listed in Table \ref{tab:haplotype_abbreviations}).
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    The pair of horizontal red lines in each plot indicate the lower and upper bound 
    of the 99\% confidence interval.
    \textbf{(B)} 
    MHC ligands from IEDB binding to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay. 
  }
  \label{fig:elution}
\end{figure}
